Synthesizing Quotient Lenses

### 2018-02-23 papers/QuotientLenses/main.tex
Tidying

let bib_to_end : (lens in bibtex $\Leftrightarrow$ end_note) =
preamble . label . author_lens . title_lens
\end{lstlisting}
\caption{An example lens between \cd{bibtex} and \cd{end_note} regular
expressions with no equivalences.}
\label{fig:example-lens}
\end{figure}

@@

\begin{figure}[t]
\centering
\includegraphics[width=\textwidth]{canonizers-outside}
\caption{Quotient Lens with ``Canonizers at the Edges''\sam{This is a
screenshot from Nate's thesis. Are we allowed to use it?}\bcp{We can
(if we put ``from [Nate's thesis]'' in the caption), but I don't think
we want the full complexity of asymmetric lenses here.  We should draw
the figure again.  (I have the OmniGraffle file for it, so this is
easy if I know how it should look.)}\bcp{Done---what do you think?}
\sam{Yes this is more accurate, except that we don't need a general choose
function. With QREs the kernel language is always contained in the whole
language so we just use the inclusion as the choose function.}}
\label{fig:attheedges}
\end{figure}

@@

\begin{figure}[p!]
\begin{center}
\AxiomC{$R$ is strongly unambiguous}
\UnaryInfC{$\wf{\mathit{id}(R)}$}
\DisplayProof
\hskip 1.5em
\AxiomC{$s \in \mathcal{L}(R)$}
\UnaryInfC{$\wf{\project{R}{s}}$}
\DisplayProof
\hskip 1.5em
\end{center}

>>>>

let bib_to_end : (lens in bibtex $\Leftrightarrow$ end_note) =
preamble . label . author_lens . title_lens
\end{lstlisting}
\caption{An example lens between \cd{bibtex} and \cd{end_note} regular
expressions with no equivalences.\bcp{Indentation needs work.  And there was
a suggestion to colorize the new keywords that we're introducing here
(including symbolic ones, I guess)}} 
\label{fig:example-lens}
\end{figure}

@@

\begin{figure}[t]
\centering
\includegraphics[width=0.7\textwidth]{canonizers-outside}
\caption{Quotient Lens with ``Canonizers at the Edges''\sam{This is a
screenshot from Nate's thesis. Are we allowed to use it?}\bcp{We can
(if we put ``from [Nate's thesis]'' in the caption), but I don't think
we want the full complexity of asymmetric lenses here.  We should draw
the figure again.  (I have the OmniGraffle file for it, so this is
easy if I know how it should look.)}\bcp{Done---what do you think?}
\sam{Yes this is more accurate, except that we don't need a general choose
function. With QREs the kernel language is always contained in the whole
language so we just use the inclusion as the choose function.}\bcp{I can
fix.}} 
\label{fig:attheedges}
\end{figure}

@@

\begin{figure}[tp!]
\begin{center}
\AxiomC{$R$ is strongly unambiguous}
\UnaryInfC{$\wf{\mathit{id}(R)}$}
\DisplayProof
\hskip 1.5em
\AxiomC{$s \in \mathcal{L}(R)$}
\UnaryInfC{$\wf{\project{R}{s}}$}
\DisplayProof
\hskip 1.5em
\end{center}
